Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-28 SRO_Retest_Analyses.Rmd
cont working on retest exploration

Trying to use `lavaan` first. It's not happy with me.
```{r}
unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")

summary(unrotated, std=TRUE)
inspect(unrotated, "std")
```

>>>>

Trying to use `lavaan` first. It's not happy with me.
```{r}
unrotated <- try(efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr"))

# summary(unrotated, std=TRUE)
# inspect(unrotated, "std")
```
